method

### 2021-08-11 06_Paper/ER-ED/method.Rmd
added text

"We report how we determined our sample size, all data exlusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]

## 2.1 Participants

@@

## 2.2

>>>>

"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]

## 2.1 Power analysis and participants

@@

## 2.2 Experimental procedure

All session took place in a shielded cabin with constant lighting. Participants received information about the

## 2.3 Emotion regulation paradigm
